Keystoneness, centrality, and the structural controllability of ecological networks

### 2018-12-12 paper/supp-info.Rmd
Settle on a title

---
title: "Structural controllability of ecological networks"
subtitle: "Supporting Information"
author: "Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
classoption: a4paper
csl: journal-of-ecology.csl
documentclass: artikel1
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{xr}
  - \externaldocument[M-]{manuscript}
  - \usepackage{multirow}
bibliography: phd-bibliography/network-control.bib
---

@@

```{r fig-correlogram, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]], fig.cap="Mean Spearman correlation coefficients between control metrics (control capcity $\\phi$ and the likelyhood of being a superior node $\\sigma$) and centrality metrics commonly used to estimate a species' 'keystoness' (closeness centrality $l$ , betwenness $w$, eigen centrality $e$, page rank $g$ and degre $k$) in each of the networks. Purple and orange tiles indicate a positive correlation or negative correlation respectively."}
drake::loadd(fig_correlation)
cowplot::plot_grid(plotlist = fig_correlation, ncol = 2)
```

>>>>

---
title: "Keystoneness, centrality, and the structural controllability of ecological networks"
subtitle: "Supporting Information"
author: "Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
classoption: a4paper
csl: journal-of-ecology.csl
documentclass: artikel1
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{xr}
  - \externaldocument[M-]{manuscript}
  - \usepackage{multirow}
bibliography: phd-bibliography/network-control.bib
---

@@

```{r fig-correlogram, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]], fig.cap="Mean Spearman correlation coefficients between control metrics (control capcity $\\phi$ and the likelihood of being a superior node $\\sigma$) and centrality metrics commonly used to estimate a species' 'keystoness' (closeness centrality $l$ , betwenness $w$, eigen centrality $e$, page rank $g$ and degre $k$) in each of the networks. Purple and orange tiles indicate a positive correlation or negative correlation respectively."}
drake::loadd(fig_correlation)
cowplot::plot_grid(plotlist = fig_correlation, ncol = 2)
```
